Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-03-15 analysis/paper/paper.Rmd
called survey site script within paper.Rmd. Runs without issue; I will need to add new captions.
Had to rearrange call to occur after calls for data_wrangling and target species data frame creation (so no object errors).

>>>>

```{r SurveySites, eval=TRUE, cache = FALSE, include = FALSE}
# dotplot of survey occurrences by unit and whether there were observations
source("../scripts/survey_sites.R", echo=FALSE)
```

```{r Fig-SurveySites, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap="The annual dates of the first and last survey have both varied by over a month across the years."}

print(plot_units_1)
```
